A fast primal-dual algorithm for computing best response strategies in two-person sequential games

### 2014-07-26 paper.tex
ENH: better convergence criterion
cosmetic

\begin{document}
%\onecolumn
\title{A fast algorithm for computing best response strategies in two-person sequential games}

@@

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\\\
$a^Tb$: \quad \textit{the dot product of two vectors $a$ and $b$}\\
$\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
$i_C$: \quad \textit{the indicator function of the convex set $C$}\\
$\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
$\|K\|_2$: \quad \textit{the matrix 2-norm of the matrix $K$}\\
$f^*$: \quad \textit{the Fenchel transform of the convex l.s.c function $f$}\\
\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
$E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}

@@

@@

\begin{algorithm}[htb]
\caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
\textbf{Let} $\epsilon > 0$ be a given tolerance.\\
\textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
$\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
\textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
\Repeat{
  $\frac{1}{k + 1}\sum_{j=0}^{k}{\|e - E\tilde{x}^{(j)}\|^2_2} < \epsilon$}{
  \begin{eqnarray*}
    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
    \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
    k &\leftarrow& k + 1
  \end{eqnarray*}
} \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
\label{Tab:pseudocode_pb}
\end{algorithm}

>>>>

\begin{document}
%\onecolumn
\title{A fast primal-dual algorithm for computing best response strategies in two-person sequential games}

@@

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,\\\\
$u^Tv$: \quad \textit{the dot product of two vectors $u$ and $v$}\\
$\mathbb{R}_+$: \quad \textit{the nonnegative part of the real-line $\mathbb{R}$}\\
$(x)_+$: \quad \textit{the component-wise maximum of the vector $x$ and 0}\\
$i_C$: \quad \textit{the indicator function of the convex set $C$}\\
$\Pi_C$: \quad \textit{the euclidean projector onto the convex set $C$}\\
$\|K\|_2$: \quad \textit{the matrix 2-norm of the matrix $K$}\\
$f^*$: \quad \textit{the Fenchel transform of the convex l.s.c function $f$}\\
\textit{l.s.c}: \quad \textit{acronyme for ``lower semi-continuous''}\\
$E^{-1}(U)$: \quad \textit{the pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$}

@@

\begin{remark}
Neither $G$ nor $F^*$ is strongly convex and so Alg.\ref{Tab:pseudocode_pb} cannot be accelerated in the sense of algorithm 39 of \cite{chambolle2010}.
\end{remark}

\begin{algorithm}[htb]
  \caption{Primal-dual algorithm for computing best response against opponent's realization plan $y_0$}
  \textbf{Given} Tolerance $\epsilon > 0$.\\
  \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
  $d^{(0)} = 0$; $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
  \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
  \Repeat{
    $d^{(k)} < \epsilon$}{
    \begin{eqnarray*}
      r^{(k)} &\leftarrow& e - E\tilde{x}^{(k)}\\ 
    \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma r^{(k)}\\
    x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
    \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
    d^{(k+1)} &\leftarrow& max(d^{(k)}, \frac{\|x^{(k+1)} - x^{(k)}\|^2_2}{2\tau} + \frac{\|r^{(k)}\|^2_2}{2})\\
    k &\leftarrow& k + 1
    \end{eqnarray*}
  } \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
  \label{Tab:pseudocode_pb}
\end{algorithm}

@@
